---
title: "code_rollingsales_bronx"
author: "Jostein Barry-Straume"
date: "6/20/2017"
output: html_document
---

## Author: Benjamin Reddy
## Taken from pages 49-50 of O'Neil and Schutt
> Provided code is fashioned to clean and explore the rolling sales of the Bronx.

# Install the necessary package(s)
```{r echo=TRUE}
library(plyr)
```

# Set working directory
```{r echo=TRUE}
setwd("/Users/Jostein/Grad School/SMU/Doing_Data_Science/unit_6/livesession6assignment")
```

[http://www1.nyc.gov/site/finance/taxes/property-rolling-sales-data.page](http://www1.nyc.gov/site/finance/taxes/property-rolling-sales-data.page)

# Read the CSV file
```{r echo=TRUE}
bk <- read.csv("/Users/Jostein/Grad School/SMU/Doing_Data_Science/unit_6/livesession6assignment/data/rollingsales_bronx.csv",skip=4,header=TRUE)
```

# Check the data
## And compactly display the internal structure
```{r echo=TRUE}
head(bk)
summary(bk)
str(bk) # Very handy function!
```

# Clean and format the data with regular expressions
```{r echo=TRUE}
bk$SALE.PRICE.N <- as.numeric(gsub("[^[:digit:]]","", bk$SALE.PRICE))
count(is.na(bk$SALE.PRICE.N))

names(bk) <- tolower(names(bk)) # make all variable names lower case
```

## Get rid of leading digits
```{r echo=TRUE}
bk$gross.sqft <- as.numeric(gsub("[^[:digit:]]","", bk$gross.square.feet))
bk$land.sqft <- as.numeric(gsub("[^[:digit:]]","", bk$land.square.feet))
bk$year.built <- as.numeric(as.character(bk$year.built))
```

## Explore the data to make sure there's not anything
## weird going on with sale prices
```{r echo=TRUE}
attach(bk)
hist(sale.price.n) 
detach(bk)
```

## Keep only the actual sales
```{r echo=TRUE}
bk.sale <- bk[bk$sale.price.n!=0,]
plot(bk.sale$gross.sqft,bk.sale$sale.price.n)
plot(log10(bk.sale$gross.sqft),log10(bk.sale$sale.price.n))
```

## for now, let's look at 1-, 2-, and 3-family homes
```{r echo=TRUE}
bk.homes <- bk.sale[which(grepl("FAMILY",bk.sale$building.class.category)),]
dim(bk.homes)
plot(log10(bk.homes$gross.sqft),log10(bk.homes$sale.price.n))
summary(bk.homes[which(bk.homes$sale.price.n<100000),])
```

## remove outliers that seem like they weren't actual sales
```{r echo=TRUE}
bk.homes$outliers <- (log10(bk.homes$sale.price.n) <=5) + 0
bk.homes <- bk.homes[which(bk.homes$outliers==0),]
plot(log10(bk.homes$gross.sqft),log10(bk.homes$sale.price.n))
```